My title

### 2024-09-18 outputs/paper/paper.qmd
Second edition of weakness

Even though our data is the most uptodate and accurate date aviliable for homeless population on opendatatoronto, it might have potential bias towards estimation the ture homeless population in city of Toronto. One clear bias is that people would not stay in the shelter everyday and they would enter and exit the shelter frequently [@toronto_shelter_data]. Correctly measure the ture popution demegraphic is a very diffcult on-going problem in Canada, but the shelter flow data would provide a proper estimate of our interest [@dionne2023review]. To understand the probelms better and develop more strategies the next steps would be to research stratgies that could reach out and survey the population that is diffcult to contact such as unsheltered homeless population. Also, a new homeless reduction plan should to develop and adopt to suit the ongoing change of demegraphic of homeless population.

>>>>

Even though our data is the most up-to-date and accurate data available for the homeless population on Opendatatoronto, it may still have a bias toward the estimation of the true homeless population in the city of Toronto. For example, people would not stay in the shelter every day and they would enter and exit the shelter frequently [@toronto_shelter_data]. Accurately measuring the true population demographic is a very difficult topic even in Canada, but the shelter flow data would provide a proper estimate of our research interest [@dionne2023review]. To understand the problems better and develop more strategies, the next steps would be to research sampling methods that could reach out and survey the population that is difficult to contact such as the unsheltered homeless population. More incorporative sampling strategies would provide us better understanding of homeless demographics and develop further sophisticated plans to reduce homelessness.
